Visual Search and Pre-crastination

### 2023-09-01 RegReport/paper.tex
added expo analysis

\begin{figure}[t]
  \centering

\subfigure[]{\includegraphics[width=6cm]{../analysis/scratch/post_plot.pdf}}
\subfigure[]{\includegraphics[width=6cm]{../analysis/scratch/pre_cras_consc.pdf}}
  \caption{(a) Posterior distributions for the mean of the two groups of participants, and the difference between them. (b) There is no evidence for a relationship between pre-crastination and conscientiousness}
  \label{fig:full_exp_strategy}
\end{figure}

@@

We now investigate whether our data suggests any new hypotheses that could be of interest to other researchers.

>>>>

\begin{figure}[t]
  \centering  
\subfigure[]{\includegraphics[width=6cm]{../analysis/scratch/post_plot.pdf}}
\subfigure[]{\includegraphics[width=6cm]{../analysis/scratch/pre_cras_consc.pdf}}
  \caption{(a) Posterior distributions for the mean of the two groups of participants, and the difference between them. (b) There is no evidence for a relationship between pre-crastination and conscientiousness}
  \label{fig:full_exp_strategy}
\end{figure}

@@

We now investigate whether our data suggests any new hypotheses that could be of interest to other researchers. We find some tentative evidence to suggest that participants who do not pre-crastinate may score slightly higher in extraversion and open-mindedness. We find no evidence of any clear relationships between the personality measures and visual search strategy.

\begin{figure}[t]
  \centering  
\includegraphics[width=10cm]{../analysis/scratch/exp_strat.pdf}
  \caption{(\textit{left}) Relationship between the pre-crasination and each of the personality measures. The effect size measures the $95\%$ confidence interval for the mean difference between participants who precrastinated and those who didn't. (\textit{right}) Correlations between our search strategy metric and the personality measures. Effect size measures the $95\%$ confidence interval in Pearson's $r$.}
   \label{fig:exp_analysis}
\end{figure}

### 2023-09-01 analysis/3_exploratory.Rmd
added expo analysis

# now to it with Bayes
library(brms)
m <- brm(n_pc ~ conscientiousness, data = dat_p,
               priors = c(prior()))

>>>>

# now to it with Bayes
library(brms)

m <- brm( conscientiousness ~ pre_crastinate, 
         data = dat_p %>% filter(pre_crastinate %in% c("yes", "no")),
               prior = c(prior(normal(0, 1), class = "Intercept"),
                          prior(normal(0, 1), class = "b")))

m <- brm( conscientiousness ~ n_pc, 
         data = dat_p,
               prior = c(prior(normal(0, 1), class = "Intercept"),
                          prior(normal(0, 1), class = "b")))
```
